\maketitle
\makesignature

\ifproject
\begin{abstractTH}
เขียนบทคัดย่อของโครงงานที่นี่

เกมแนวสยองขวัญที่ใช้ความร่วมมือของผู้เล่นสองคน พัฒนาขึ้นเพื่อนำเสนอเกมสยองขวัญในรูปแบบใหม่ที่ให้ผู้เล่นช่วยกันฟันฝ่าอุปสรรค และทำภารกิจให้สำเร็จไปด้วยกัน ความเชื่อยุคกลางมีอยู่ว่า ปีศาจปลอมแปลงเป็นสัตว์ได้หลายชนิด อาศัยอยู่ในป่ารกร้าง ผู้เล่นจะสวมบทบาทเป็นทีมปราบปีศาจในป่ารกร้างเพื่อให้ชุมชนละแวกนั้นปลอดภัย เกมนี้มีการออกแบบให้สามารถเล่นซ้ำได้เรื่อย ๆ เพื่อมอบประสบการณ์ใหม่ ๆ และท้าทายให้กับผู้เล่นในทุกครั้งที่เล่น ไม่ว่าจะเป็นฉาก ภูมิประเทศที่เปลี่ยนไปจากเดิม ปีศาจ และกลยุทธการปราบปีศาจ เกมนี้พัฒนาโดยใช้ Unreal Engine เพื่อให้ผู้เล่นได้สัมผัสประสบการณ์ที่สมจริงผ่านมุมมอง \\ บุคคลที่หนึ่ง กลุ่มผู้เล่นเป็นช่วงอายุมากกว่า 18 ปี
\end{abstractTH}

\begin{abstract}
Two-player Cooperative Horror Game is developed to present a new type of horror game that allows players to cooperate with each other to overcome obstacles and complete missions together. Based on medieval beliefs that demons can disguise themselves as animals and live in the wilderness, players assume the roles of a team fighting evil to keep the people safe. Designed to be replayable, the game offers a new and challenging experience each time it's played, with changing scenes, terrain, demons, and strategies to defeat them. The game has been developed using the Unreal Engine to provide players with an immersive first-person perspective. The target player is aged 18 and over.
\end{abstract}

\iffalse
\begin{dedication}
This document is dedicated to all Chiang Mai University students.

Dedication page is optional.
\end{dedication}
\fi % \iffalse

\begin{acknowledgments}
Your acknowledgments go here. Make sure it sits inside the
\texttt{acknowledgment} environment.

\acksign{2020}{5}{25}
\end{acknowledgments}%
\fi % \ifproject

\contentspage

\ifproject
\figurelistpage

\tablelistpage
\fi % \ifproject

% \abbrlist % this page is optional

% \symlist % this page is optional

% \preface % this section is optional
